### 2013-09-15 results.tex
fixed refs to table and figs

The computed volumes of the prostates from the MR and ARFI imaging data are
presented in Table~\ref{tab:fig_mr_arfi_volumes}.  The subvolumes associated
with the zonal anatomy in each imaging modality was measured
(Figure~\ref{fig:fig_mr_arfi_volumes}(a)), showing an mean overestimation of
total prostate volume of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:fig_mr_arfi_volumes}(b)), and a relative
underestimation of the central zone volume relative to the central gland in MR
imaging of -15.3 $\pm$ 13.0 \% (Figure~\ref{fig:fig_mr_arfi_volumes}(c)).

>>>>

The computed volumes of the prostates from the MR and ARFI imaging data are
presented in Table~\ref{tab:mr_arfi_volumes}.  The subvolumes associated
with the zonal anatomy in each imaging modality was measured
(Figure~\ref{fig:mr_arfi_volumes}(a)), showing an mean overestimation of
total prostate volume of 36.7 $\pm$ 27.9\% by ARFI imaging compared to MR
volumes (Figure~\ref{fig:mr_arfi_volumes}(b)), and a relative
underestimation of the central zone volume relative to the central gland in MR
imaging of -15.3 $\pm$ 13.0 \% (Figure~\ref{fig:mr_arfi_volumes}(c)).
